\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-15 report/paper.tex
fix to equation in boundary condition

\begin{eqnarray}
\label{eqn:quadratic}
f(x,y,z) &=& Ax^2+2Bxy+2Cxz\\
\nonumber &+&2Dx+Ey^2+2Fyz\\
\nonumber &+&2Gy+Hz^2+2Iz\\
\nonumber &+&J
\end{eqnarray}

@@

Since the quadric surface is known analytically can the differentiation be applied to the quadric directly to get the gradient of the shape in position $\vect{x}$. This gives an efficient and analytical expression with a coefficient matrix $Q$, which is used to determine the new velocity direction of a particle after colliding with the surface.

\begin{eqnarray}
\nabla f(x,y,z)
\label{eqn:quadricnormal}
\nonumber = 2 \left[ \begin{array}{cccc}
A & B & C &D\\
B & E & F & G\\
C & F & H & I\\
 \end{array} \right] \left[ \begin{array}{c}x \\
y \\
z \\
1 \end{array} \right]\\
\nonumber = 2\mathbf{Q}_{sub}\mathbf{p}
\end{eqnarray}

>>>>

\begin{eqnarray}
\label{eqn:quadratic}
f(x,y,z) &=
\nonumber & Ax^2+2Bxy+2Cxz\\
 &+&2Dx+Ey^2+2Fyz\\
\nonumber &+&2Gy+Hz^2+2Iz\\
\nonumber &+&J
\end{eqnarray}

@@

Since the quadric surface is known analytically can the differentiation be applied to the quadric directly to get the gradient of the shape in position $\vect{x}$. This gives an efficient and analytical expression with a coefficient matrix $Q$, which is used to help determine the new velocity direction of a particle after colliding with the surface.

\begin{eqnarray}
\label{eq:quadricnormal}
\nabla f(x,y,z) = 2 \left[ \begin{array}{cccc}
A & B & C &D\\
B & E & F & G\\
C & F & H & I\\
 \end{array} \right] \left[ \begin{array}{c}x \\
y \\
z \\
1 \end{array} \right]\\
\nonumber = 2\mathbf{Q}_{sub}\mathbf{p}
\end{eqnarray}
